Mass and occupation fraction of dark matter halos hosting Lyman-$\alpha$ emitters at $z\sim 3$

### 2014-01-06 paper/ms.tex
reviewed discussion

Out of the initial set of $9000$ models we end up with $40$ that are
consistent with the observational constraints. To facilitate the
discussion of these models we define a new quantity, the halo mass
range $\Delta M=\log_{10}M_{\rm max} - \log_{10}M_{\rm  min}$, which
together with the occupation fraction, $f_{\rm occ}$, and the minimum
mass $M_{\rm min}$ allows us to classify all the successful models into
three families:

@@

{\bf The models in the third family are barely consistent with the
  constraints from the ACF. They have mean values of $\theta_0$
  outside the observational uncertainties, but have
  are considered as consistent because their large error bars overlap. These
  models they have another particular feature: their minimum mass is
  exactly $M_{\rm min}=10^{10.9}\hMsun$. Because these models are
  are barely compatible with observations and are a minority of the
  consistent models, we exclude them from the rest of the discussion.}

\subsection{Two relevant features}
There are two interesting features in the remaining two first
families. First, the occupation fraction can take any value from $0.1$
to $1.0$. Second, the halos hosting LAEs all have a narrow mass range
$\Delta M\leq 1.0$.

{\bf The existence of models with high occupation fractions $f_{\rm
    occ}>0.2$ is unexpected from previous clustering analysis that do
  not take  account the effect of cosmic variance in the same way we
  propose in this \documentname. Nevertheless, the mass range
  predicted by our models is consistent with already published
  observational results. This suggests that taking explicitly cosmic
  variance into account hinders the possibility of constraining the
  LAEs occupation fraction.}

{\bf Concerning the narrow mass range $\Delta M
  <1.0$ the question arises of how can we give a physical
  interpretation for the existence of such  a narrow mass range. We
  can start with a reasonable   assumption. Namely that star formation
  rate increases with halo's  mass.}

Under this assumption the cut at the low mass end, $M_{\rm min}$, can be
interpreted in terms of the minimal star formation rate required to
produce a \ly luminosity above observational detection thresholds.  
A cut at higher halo masses $M_{\rm  max}$ requires a
different justification. There are two complementary physical
scenarios that could provide

@@

\subsection{Comparison to other clustering estimates}

@@

Our results are in a general good agreement with those estimates for
the host mass. This is not completely unexpected given that we have
also required consistency with ACF measurements. These expectations
are {\bf mostly} matched by the first family of models, also summarized in Table
\ref{table:firstfamily}. These models, which favor only the 
low occupations fractions, are also consistent in that regards with
the observational expectations.

The novelty in our results is that we have a detailed estimate for 
host halo mass range together with the escape fraction. This allows us
to show that the halo mass range can, in some cases, be narrow $\Delta M <
0.3$dex, something that cannot be inferred from ACF analysis alone.
Furthermore, In contrast to \citep{Gawiser07} and \citep{Ouchi2010} we
find that an ACF analysis on a single data-set is not enough to rule
out models with a high occupation fraction $f_{\rm occ}>0.3$, which
represent half of our best models.

@@

There are four caveats for the work presented here that are important
to keep in mind. The first is the  
assumption of a single LAE per dark matter halo. This contradicts the
general expectation of dark matter sub-halos in the simulation to host
satellite galaxies. However, it has been found in analysis based on
the shape of the correlation function \citep{Jose2013b} that satellite
galaxies are not a dominant population, making our initial
approximation a reasonable one. {\bf The lack of close pairs in
  observations is another hint that the observed LAE population matches}
Therefore we conclude that including
the effect of satellite galaxies does not change the main results
reported in this \documentname.

>>>>

Out of the initial set of $9000$ models we end up with $40$ that are
consistent with the observational constraints. To facilitate the
discussion of these models we define a new quantity, the halo mass
range $\Delta M\equiv \log_{10}M_{\rm max} - \log_{10}M_{\rm  min}$, which
together with the occupation fraction, $f_{\rm occ}$, and the minimum
mass $M_{\rm min}$ allows us to classify all the successful models into
three families:

@@

{\bf The models in the third family are barely consistent with the
  constraints from the ACF. They have values of $\beta$ close to $1.0$
  (instead of the observational value of $0.8$) and $\theta_0$ on the
  range of $13^{\prime}$ (the mean observational value is close to
  $8^{\prime}$) but are considered
  consistent because their large error bars barely overlap with the
  observational expectation. These 
  models they have another particular feature: their minimum mass is
  exactly $M_{\rm min}=10^{10.9}\hMsun$. Because these models are
  are barely compatible with observations and are a minority of the
  consistent models, we exclude them from the rest of the discussion.}

\subsection{Two relevant features in the preferred models}
There are two interesting features in the remaining two first
families. First, the occupation fraction can take any value from $0.1$
to $1.0$. Second, the halos hosting LAEs all have a narrow mass range
$\Delta M\leq 1.0$.

{\bf The existence of models with high occupation fractions $f_{\rm
    occ}>0.2$ is unexpected from previous clustering analysis that do
  not take  account the effect of cosmic variance in the same way we
  propose in this \documentname. Nevertheless, the mass range
  predicted by our models is consistent with already published
  observational results \citep{Gawiser07,Ouchi2010}. This suggests
  that explicitly taking cosmic variance of the observed fields into
  account (the only point not included in the analysis already cited)
  hinders the possibility of constraining the LAEs occupation
  fraction.}

{\bf Concerning the narrow mass range $\Delta M
  <1.0$ the question arises of how can we give a physical
  interpretation for the existence of such  a narrow mass range. We
  can start with a reasonable   assumption. Namely that star formation
  rate increases with halo's  mass. Under this assumption the cut at
  the low mass end, $M_{\rm min}$, can be interpreted in terms of the
  minimal star formation rate required to produce a \ly luminosity
  above observational detection thresholds.   A cut at higher halo
  masses $M_{\rm  max}$ requires a different justification. There are
  two complementary physical scenarios that could provide it.}

@@

\subsection{Comparison to previous clustering estimates}

@@

Our results are in a general good agreement with those estimates for
the host mass. This is not completely unexpected given that we have
also required consistency with ACF measurements. These expectations
are {\bf mostly} matched by the first family of models, also summarized in Table
\ref{table:firstfamily}. These models, which favor only the 
low ($\sim 10\%$) occupations fractions, are also consistent in that
       regards with the observational expectations by \cite{Gawiser07}.

The novelty in our results is that we have a detailed estimate for 
host halo mass range together with the escape fraction. This allows us
to show that the halo mass range can, in some cases, be narrow $\Delta M <
0.3$ dex, something that cannot be inferred from ACF analysis alone.
Furthermore, In contrast to \cite{Gawiser07} and \cite{Ouchi2010} we
find that an ACF analysis is not enough to rule
out models with a high occupation fraction $f_{\rm occ}>0.3$, which
represent half of our best models.

@@

There are four caveats for the work presented here that are important
to keep in mind. The first is the  
assumption of a single LAE per dark matter halo. This contradicts the
general expectation of dark matter sub-halos in the simulation to host
satellite galaxies. However, it has been found in analysis based on
the shape of the correlation function \citep{Jose2013b} that satellite
galaxies are not a dominant population, making our initial
approximation a reasonable one. {\bf The lack of close pairs in
  observations is another hint that the observed LAE population matches}
Therefore we conclude that including the effect of satellite galaxies
should not significantly change the main results reported in this
\documentname.
